Figure 3. Tissue Microbiome Abundances

### 2022-01-06 reports/rmarkdown/manuscript/Figure3.Rmd
correcting total abundance and adding colour coding

  par(mar=c(1,5,1,1.5)) #b,l,t,r
  temp[is.nan(temp)] <- 0

  o <- order( rowSums(temp_legend) , decreasing = T)
  sample_o <- names(group_annotation)[ order( group_annotation )]
  temp <- temp[o,sample_o]*100
  temp <- rbind(temp[c(lvl[1:16]),], Other = colSums(temp[!(row.names(temp) %in% c(lvl[1:16])), ]))

  barplot( temp, las=2 , border = NA , yaxs="i", xaxs="i",ylab="abundance",
           main=gsub("_gr","",i[1]),font.main=1,names.arg = rep("",ncol(temp)),
           col = taxa_pal[factor(rownames(temp),levels = lvl)])
  points( (1:ncol(temp))*1.2 -.5, rep(par("usr")[3],ncol(temp))-2, bg="white",
        col= c("tomato","orange","#d7d7d7")[as.numeric(metadata$BV_Diagnosis_v3)][order( group_annotation)],
        pch=15,cex=.7,xpd=T)
  points( (1:ncol(temp))*1.2 -.5, rep(par("usr")[3],ncol(temp))-8,bg="white",
        col= c("#d7d7d7","tomato")[as.numeric(metadata$HIVstatus)][order( group_annotation )],
        pch=15,cex=.7,xpd=T)
  text(par("usr")[2],par("usr")[3]-2,labels = "      BV",cex=.5,xpd=T)
  text(par("usr")[2],par("usr")[3]-8,labels = "       HIV",cex=.5,xpd=T) # pos=4,
}

@@

r <- raw_list %>%
  map(., ~mutate(.,across(where(is.numeric), ~ ./sum(.))) ) %>%
  map(., ~(rowSums(.x)/length(colnames(.x)) )*100 ) %>%
  bind_rows(., .id="ID") %>%
    pivot_longer(-ID) %>% 
    pivot_wider(names_from = ID, values_from = value) %>%
    mutate_at(vars(name), ~replace(., ASV_CVL_V3<0.5514392, "Other")) %>%
    group_by(name) %>%
    summarize(across(where(is.numeric), ~sum(.))) %>%
    arrange(-ASV_CVL_V3) %>%
    dplyr::rename(Luminal="ASV_CVL_V3",Tissue="ASV_tissue_V3") %>%
    `row.names<-`(., NULL) %>% 
    column_to_rownames(var = "name") %>%
    as.matrix()

par(mar=c(6,5,2,.3)) #b,l,t,r
barplot( r, border = NA ,ylab="abundance", xlab ="", axisnames = F,
         col = taxa_pal[factor(rownames(r),levels = rownames(r))])
title(main = "Total relative abundance ", line = 0.5, cex.main = .9, font.main= 1)
mtext("Luminal        Tissue ", line = 0, cex=.6, side=1)

>>>>

  par(mar=c(1.5,5,1,1.5)) #b,l,t,r
  temp[is.nan(temp)] <- 0

  o <- order( rowSums(temp) , decreasing = T)
  sample_o <- names(group_annotation)[ order( group_annotation )]
  temp <- temp[o,sample_o]*100
  temp <- rbind(temp[c(lvl[1:16]),], Other = colSums(temp[!(row.names(temp) %in% c(lvl[1:16])), ]))

  barplot( temp, las=2 , border = NA , yaxs="i", xaxs="i",ylab="abundance",
           main=gsub("_gr","",i[1]),font.main=1,names.arg = rep("",ncol(temp)),
           col = taxa_pal[factor(rownames(temp),levels = lvl)])

  points( (1:ncol(temp))*1.2 -.5, rep(par("usr")[3],ncol(temp))-2, 
          bg="white", pch=15,cex=.7,xpd=T, 
          col= c("tomato","orange","#d7d7d7")[as.numeric(metadata$BV_Diagnosis_v3)][order( group_annotation)])
  points( (1:ncol(temp))*1.2 -.5, rep(par("usr")[3],ncol(temp))-7,bg="white",
        col= c("#d7d7d7","tomato")[as.numeric(metadata$HIVstatus)][order( group_annotation )],
        pch=15,cex=.7,xpd=T)
  text(par("usr")[2],par("usr")[3]-2,labels = "      BV",cex=.5,xpd=T)
  text(par("usr")[2],par("usr")[3]-7,labels = "       HIV",cex=.5,xpd=T) # pos=4,

 l <- c("BV:","Normal","Intermediate","BV")
  legend(x = 10, y = 111, #"bottom", inset = c(0, -0.5),
         bty = "n", horiz=TRUE, cex=0.7, xpd = T, 
         border = "white", 
         legend = l, x.intersp=0.5, xjust=0,
         text.width = c(0, map_dbl(l, ~strwidth(.x)/2)) ,
         fill=c(NA, "#d7d7d7","orange","tomato"))
  l2 <- c("HIV:","HIV-","HIV+")
  legend(x = 70, y = 111, # bottom position: par("usr")[3]-5
         bty = "n", horiz=TRUE, cex=0.7, xpd = T,
         border = "white",
         legend = l2, x.intersp=0.5, 
         text.width =c(0, map_dbl(l2, ~strwidth(.x)/2)),
         fill=c(NA, "#d7d7d7", "tomato"))
}

@@

r <- raw_list %>%
  map(., ~mutate(.,across(where(is.numeric), ~ ./sum(.))) ) %>%
  map(., ~(rowSums(.x)/length(colnames(.x)) )*100 ) %>%
  bind_rows(., .id="ID") %>%
    pivot_longer(-ID) %>% 
    pivot_wider(names_from = ID, values_from = value) %>%
    mutate_at(vars(name), ~replace(., ASV_CVL_V3<0.55, "Other")) %>%
    group_by(name) %>%
    summarize(across(where(is.numeric), ~sum(.))) %>%
    arrange(-ASV_CVL_V3) %>%
    dplyr::rename(Luminal="ASV_CVL_V3",Tissue="ASV_tissue_V3") %>%
    `row.names<-`(., NULL) %>% 
    column_to_rownames(var = "name") %>%
    as.matrix()

par(mar=c(6,5,2,.3)) #b,l,t,r
barplot( r, border = NA ,ylab="abundance", xlab ="", axisnames = F,
         col = taxa_pal[factor(rownames(r),levels = lvl)])
title(main = "Total relative abundance ", line = 0.5, cex.main = .9, font.main= 1)
mtext("Luminal        Tissue ", line = 0, cex=.6, side=1)
